Women in Film

### 2017-07-17 draft_post.Rmd
Cleaning, cleaning, and more cleaning

```{r pronoun_ratio, echo = FALSE, dependson="pronoun_bigrams", fig.width=8, fig.height=8}
pronoun_ratio <- pronoun_bigrams %>%
    count(word1, word2) %>%
    spread(word1, n, fill = 0) %>%
    mutate(total = he + she,
           he = (he + 1) / sum(he + 1),
           she = (she + 1) / sum(she + 1),
           logratio = log2(she / he)) %>%
    arrange(desc(logratio)) %>%
    filter(nchar(word2) > 2,
           !(word2 %in% c("door", "ad", "he", "1s", "lp",
                          "car", "himself", "pans", "dead", 
                          "queen", "back", "too", "were",
                          "doesn", "half")))

@@

```{r, echo = FALSE, dependson="pronoun_ratio"}
example_text <- pronoun_ratio %>% 
    top_n(800, total) %>% 
    head(20) %>% 
    select(word = word2) %>%
    bind_rows(data_frame(word = c("cleans", "moans", "laughs", "twirls",
                                  "lingers", "bursts", "retreats", "answer",
                                  "creeps"))) %>%
    bind_rows(pronoun_ratio %>% 
                  top_n(800, total) %>% 
                  tail(20) %>% 
                  select(word = word2))

example_text
```

>>>>

```{r pronoun_ratio, echo = FALSE, dependson="pronoun_bigrams", fig.width=8, fig.height=8}
pronoun_ratio <- pronoun_bigrams %>%
    count(word1, word2) %>%
    spread(word1, n, fill = 0) %>%
    mutate(total = he + she,
           he = (he + 1) / sum(he + 1),
           she = (she + 1) / sum(she + 1),
           logratio = log2(she / he)) %>%
    arrange(desc(logratio)) %>%
    filter(nchar(word2) > 2,
           !(word2 %in% c("door", "ad", "he", "1s", "lp",
                          "car", "himself", "pans", "dead", 
                          "queen", "back", "too", "were",
                          "doesn", "half", "with", "been", 
                          "who", "she", "the")))

@@

```{r, echo = FALSE, dependson="pronoun_ratio"}
example_words <- pronoun_ratio %>% 
    top_n(800, total) %>% 
    head(20) %>% 
    select(word = word2) %>%
    bind_rows(data_frame(word = c("cleans", "moans", "laughs", "twirls",
                                  "lingers", "bursts", "retreats", "answer",
                                  "creeps", "types", "attacks", "inhales",
                                  "stares", "grimaces", "suddenly", "stops",
                                  "ducks", "waits", "stomps", "remembers",
                                  "scrambles", "splashes", "jerks", "throws",
                                  "knows", "exhales", "coughs", "flops",
                                  "crouches", "staggers", "forgets", "slashes"))) %>%
    bind_rows(pronoun_ratio %>% 
                  top_n(800, total) %>% 
                  tail(20) %>% 
                  select(word = word2))

pronouns <- c(sample(c("she", "She"), size = 36, replace = TRUE), 
              sample(c("he", "He"), size = 36, replace = TRUE))

example_text <- example_words %>%
    mutate(pronoun = pronouns,
           phrase = str_c(pronoun, word, sep = " ")) %>%
    pull(phrase) %>%
    map_df(function(x) all_lines %>%
               filter(str_detect(text, x)) %>%
               sample_n(1) %>%
               select(text)) %>%
    bind_cols(example_words) %>%
    select(word, text)

write_csv(example_text, "./example_texts.csv")
```
